### 2025-07-19 paper/sections/other/grids.qmd
adjusted Algorithm 1 and ensured consistet capitalization for CT, AR, CE etc.

Overall, we find that counterfactual training (CT) achieves it key objectives consistently across all hyperparameter settings and also broadly across datasets: plausibility is improved by up to ~60 percent (%) for the *Circles* data (e.g. @fig-grid-gen_params-plaus-circles), ~25-30% for the *Moons* data (e.g. @fig-grid-gen_params-plaus-moons) and ~10-20% for the *Linearly Separable* data (e.g. @fig-grid-gen_params-plaus-lin_sep). At the same time, the average costs of faithful counterfactuals are reduced in many cases by around ~20-25% for  *Circles* (e.g. @fig-grid-gen_params-cost-circles) and up to ~50% for *Moons* (e.g. @fig-grid-gen_params-cost-moons). For the *Linearly Separable* data, costs are generally increased although typically by less than 10% (e.g. @fig-grid-gen_params-cost-lin_sep), which reflects a common tradeoff between costs and plausibility [@altmeyer2024faithful].

>>>>

Overall, we find that counterfactual training achieves it key objectives consistently across all hyperparameter settings and also broadly across datasets: plausibility is improved by up to 60 percent (%) for the *Circles* data (e.g. @fig-grid-gen_params-plaus-circles), 25-30% for the *Moons* data (e.g. @fig-grid-gen_params-plaus-moons) and 10-20% for the *Linearly Separable* data (e.g. @fig-grid-gen_params-plaus-lin_sep). At the same time, the average costs of faithful counterfactuals are reduced in many cases by around 20-25% for  *Circles* (e.g. @fig-grid-gen_params-cost-circles) and up to 50% for *Moons* (e.g. @fig-grid-gen_params-cost-moons). For the *Linearly Separable* data, costs are generally increased although typically by less than 10% (e.g. @fig-grid-gen_params-cost-lin_sep), which reflects a common tradeoff between costs and plausibility [@altmeyer2024faithful].
